ManuscriptPURFits

### 2024-02-12 Code/ManuscriptPURFits.Rmd
Testing adding fits to 1 plot

# model with dummy dark, 0 PAR,  growth rates. Also removed data if no growth occurred for an O2 and photoperiod combination so that the model including all photoperiods would not be skewed towards zero. As per Amanda and Doug's advice, filtered out PUR d-1 above 2.0e+06 because only photoperiods greater than 4 hrs have PUR d-1 above.
PURPARStrainO2NestModels_filtered <- PURPARFits_dummy |>
  mutate(remove = case_when(Strain == "MED4" & Photoperiod == 4 ~ 1,
                            Strain == "MED4" & O2_uM == 25 & Photoperiod == 8 & WL == "WW" ~ 1,
                            Strain == "MIT9313" & O2_uM == 2.5 & Photoperiod == 16 ~ 1,
                            Strain == "MIT9313" & O2_uM == 2.5 & Photoperiod == 12 & WL == "WW" ~ 1,
                            Strain == "SS120"  & O2_uM == 2.5 & Photoperiod %in% c(16,8,4) ~ 1,
                            Strain == "SS120"  & O2_uM == 25 & Photoperiod %in% c(16) & WL == 450 ~ 1,
                            Strain == "SS120"  & O2_uM == 250 & Photoperiod %in% c(4) & WL == 450 ~ 1,
                            TRUE ~ 0)) |>
   filter(remove == 0,
          PURPhotonDose_day <= 2.0e+06) |>
  nest(data = -c("Strain","O2_uM")) |>
  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
                              data = .x,
                              start = list(a = 1e-7, b = 1e-8, Pmax = 1), 
                              lower = c(0, 0, 0),
                              upper = c(1,1,100),
                              control = list(maxiter = 500)
                         ), NULL)
                         )
         ) |>
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         ) |>
  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
                              data = .x,
                              start = LinEqnStart
                         ), NULL)
                         )
         ) |>
  mutate(GRClm_Param = map(GRClm_Model, tidy),
         GRClm_Predict = map(GRClm_Model, possibly(augment)),
         GRClm_Glance = map(GRClm_Model, possibly(glance))
         )

# Nest all data before photoperiods with no growths were filtered out
NoFilter <- PURPARFits_dummy |>
   filter(PURPhotonDose_day <= 2.0e+06) |>
  mutate(Photoperiod_all = Photoperiod) %>% 
  nest(Data_all = -c("Strain","O2_uM"))

 # Join nested df with all data to df containing filtered data 
  PURPARStrainO2NestModels_filtered <- full_join(PURPARStrainO2NestModels_filtered, NoFilter) %>% 
    rename(Data_filtered = 'data')

@@

PURPARStrainO2PhotoNestModels <- PURPARFits_dummy |>
   filter(PURPhotonDose_day <= 2.0e+06) |>
 nest(data = -c("Strain","O2_uM", "Photoperiod")) |>
  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
                              data = .x,
                              start = list(a = 1e-8, b = 1e-9, Pmax = 1),
                              lower = c(-0, 0, 0),
                              upper = c(1,1,100),
                              control = list(maxiter = 500)
                         ), NULL)
                         )
         ) |>
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         ) |>
  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
                              data = .x,
                              start = LinEqnStart
                         ), NULL)
                         )
         ) |>
  mutate(GRClm_Param = map(GRClm_Model, tidy),
         GRClm_Predict = map(GRClm_Model, possibly(augment)),
         GRClm_Glance = map(GRClm_Model, possibly(glance))
         )

@@

UnnestTest <- PURPARStrainO2NestModels_filtered %>% 
  # unnest(Data_all, names_sep = "_", keep_empty = TRUE) %>% 
  unnest(GRCplatt_Predict, keep_empty = TRUE)

@@

PURPARStrainO2NestModels_filtered|>
  filter(!map_lgl(GRCplatt_Model, is.null)) |>
  unnest(GRCplatt_Predict, Data_filtered) |>
   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
  facet_grid(rows = vars(O2_uM), cols = vars(Strain)) + 
  labs(title = "PURPARStrainO2NestModels_filtered Platt") +
  theme_bw()

@@

# O2 nested data frame containing the single fit of pooled photoperiods 
 #filter to keep platt models
KeepPlattModel <- PURPARStrainO2NestModels_filtered|>
  select(-c(GRClm_Glance, GRClm_Model, GRClm_Param, GRClm_Predict)) |>
   filter(!map_lgl(GRCplatt_Model, is.null))

#filter to keep only the models that failed to fit a platt model, fits by lm remains. 
KeepLmModel <- PURPARStrainO2NestModels_filtered|>
  filter(map_lgl(GRCplatt_Model, is.null)) |>
 select(-c(GRCplatt_Glance, GRCplatt_Model, GRCplatt_Param, GRCplatt_Predict))

@@

 remove(KeepPlattModel)
 remove(KeepLmModel)
 # remove(StrainO2Photoperiod_AllModels)
 # remove(StrainO2_AllModels)

@@

# Unnest predict df for each photoperiod in order to plot fitted 
```{r}
Unnest_16 <- AllFitsCombined %>% 
  select(c(Strain, O2_uM, Predict_16)) %>%  
  unnest(Predict_16, keep_empty = TRUE) %>% 
  mutate(FitCategory = "Photoperiod16")

Unnest_12 <- AllFitsCombined %>% 
  select(c(Strain, O2_uM, Predict_12)) %>%  
  unnest(Predict_12, keep_empty = TRUE) %>% 
  mutate(FitCategory = "Photoperiod12")

Unnest_8 <- AllFitsCombined %>% 
  select(c(Strain, O2_uM, Predict_8)) %>%  
  unnest(Predict_8, keep_empty = TRUE) %>% 
  mutate(FitCategory = "Photoperiod8")

Unnest_4 <- AllFitsCombined %>% 
  select(c(Strain, O2_uM, Predict_4)) %>%  
  unnest(Predict_4, keep_empty = TRUE) %>% 
  mutate(FitCategory = "Photoperiod4")

Unnest_all <- AllFitsCombined %>% 
  select(c(Strain, O2_uM, Predict_all, Data_all)) %>% 
  # unnest(Data_all, keep_empty = TRUE) %>% 
  unnest(Predict_all, keep_empty = TRUE) %>% 
  mutate(FitCategory = "Pooled")

ForFitPlots <- bind_rows(Unnest_all, Unnest_16, Unnest_12, Unnest_8, Unnest_4)

remove(Unnest_16, Unnest_12, Unnest_8, Unnest_4, Unnest_all)

@@

  geom_line(aes(x = PURPhotonDose_day, y = .fitted), data = . %>% filter(FitCategory == "Pooled"), size = 1) + 
  geom_line(aes(x = PURPhotonDose_day, y = .fitted, linetype = "twodash"), data = . %>% filter(FitCategory == "Photoperiod16" & O2_uM == 25), size = 0.5) +
  geom_line(aes(x = PURPhotonDose_day, y = .fitted, linetype = "dotdash"), data = . %>% filter(FitCategory == "Photoperiod8"), size = 0.5) +
  geom_line(aes(x = PURPhotonDose_day, y = .fitted,  linetype = "aa"), data = . %>% filter(FitCategory == "Photoperiod4"), size = 0.5) +
  # geom_line(aes(x = PURPhotonDose_day, y = .fitted, shape = as.factor(Photoperiod), linetype = as.factor(Photoperiod)), data = . %>% filter(FitCategory == "Photoperiod4"), size = 0.5) +

@@

   scale_linetype_manual(values = c("solid", "twodash", "dotted","dotdash", "aa"),labels = c("Pooled", "16 hr", "12 hr", "8 hr", "4 hr")) +

@@

# Remove the photoperiods from the model that are significantly different from the ANOVA run on the single fit against each individual photoperiod.   
```{r}
# model with dummy dark, 0 PAR,  growth rates. Also removed data if no growth occurred for an O2 and photoperiod combination so that the model including all photoperiods would not be skewed towards zero. As per Amanda and Doug's advice, filtered out PUR d-1 above 2.0e+06 because only photoperiods greater than 4 hrs have PUR d-1 above.
PURPARStrainO2NestModels_filteredPhotoperiods <- PURPARFits_dummy |>
  mutate(remove = case_when(Strain == "MED4" & Photoperiod == 4 ~ 1,
                            Strain == "MED4" & O2_uM == 25 & Photoperiod == 8 & WL == "WW" ~ 1,
                            Strain == "MIT9313" & O2_uM == 2.5 & Photoperiod == 16 ~ 1,
                            Strain == "MIT9313" & O2_uM == 2.5 & Photoperiod == 12 & WL == "WW" ~ 1,
                            Strain == "SS120"  & O2_uM == 2.5 & Photoperiod %in% c(16,8,4) ~ 1,
                            Strain == "SS120"  & O2_uM == 25 & Photoperiod %in% c(16) & WL == 450 ~ 1,
                            Strain == "SS120"  & O2_uM == 250 & Photoperiod %in% c(4) & WL == 450 ~ 1,
                            TRUE ~ 0)) |>
   filter(remove == 0,
          PURPhotonDose_day <= 2.0e+06) |>
  mutate(removephotoperiod =  case_when(Strain == "MED4" & Photoperiod == 4 ~ 1,
                                        Strain == "MED4" & O2_uM == 250 & Photoperiod == 8 ~ 1,
                                        Strain == "MED4" & O2_uM == 25 & Photoperiod == 16 ~ 1,
                                        Strain == "MIT9313" & Photoperiod == 4 ~ 1,
                                        Strain == "MIT9313" & O2_uM == 25 & Photoperiod %in% c(8,12) ~ 1,
                                        Strain == "MIT9313" & O2_uM == 2.5 & Photoperiod %in% c(12,16) ~ 1,
                                        Strain == "SS120" & Photoperiod == 4 ~ 1,
                                        Strain == "SS120"  & O2_uM == 250 & Photoperiod %in% c(8,12) ~ 1,
                                        Strain == "SS120"  & O2_uM == 25 & Photoperiod %in% c(8) ~ 1,
                                        Strain == "SS120"  & O2_uM == 2.5 & Photoperiod %in% c(8) ~ 1,
                                        TRUE ~ 0))  |>
  filter(removephotoperiod == 0,
          PURPhotonDose_day <= 2.0e+06) |>
  nest(data = -c("Strain","O2_uM")) |>
  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
                              data = .x,
                              start = list(a = 1e-7, b = 1e-8, Pmax = 1), 
                              lower = c(0, 0, 0),
                              upper = c(1,1,100),
                              control = list(maxiter = 500)
                         ), NULL)
                         )
         ) |>
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         ) |>
  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
                              data = .x,
                              start = LinEqnStart
                         ), NULL)
                         )
         ) |>
  mutate(GRClm_Param = map(GRClm_Model, tidy),
         GRClm_Predict = map(GRClm_Model, possibly(augment)),
         GRClm_Glance = map(GRClm_Model, possibly(glance))
         )

Want platt model for all fits that did not fail and lm for platt models that returned a NULL
```{r}

 #filter to keep platt models
KeepPlattModel <- PURPARStrainO2NestModels_filteredPhotoperiods|>
  select(-c(GRClm_Glance, GRClm_Model, GRClm_Param, GRClm_Predict)) |>
   filter(!map_lgl(GRCplatt_Model, is.null))

#filter to keep only the models that failed to fit a platt model, fits by lm remains. 
KeepLmModel <- PURPARStrainO2NestModels_filteredPhotoperiods|>
  filter(map_lgl(GRCplatt_Model, is.null)) |>
 select(-c(GRCplatt_Glance, GRCplatt_Model, GRCplatt_Param, GRCplatt_Predict))

 StrainO2filteredPhotoperiod_PlattLmModel <- StrainO2_AllModels|>
  # select(-c(data)) |>
  pivot_longer(cols = -c(Strain, O2_uM, data)) |>
  drop_na(value) |>
  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param") | str_detect(name, pattern = "Predict")) |>
  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
  pivot_wider(names_from = Output, values_from = value) |>
  filter(!map_lgl(Model, is.null)) |>
  filter(!map_lgl(Glance, is.null)) |>
  mutate(AIC = map_dbl(Glance, possibly(~ as.numeric(pluck(.x, "AIC"))))) |>
  group_by(Strain, O2_uM) |>
  filter(AIC == min(AIC)) |>
  ungroup() |>
  select(-c(Glance))|>
  unnest(Param) |>
  select(-c(statistic)) |>
  pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))

 remove(KeepPlattModel)
 remove(KeepLmModel)
 # remove(PURPARStrainO2NestModels_filtered)
 # remove(PURPARStrainO2PhotoNestModels)

```{r plot new models}

StrainO2filteredPhotoperiod_PlattLmModel |>
  unnest(Predict, data) |>
  mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         WL= factor(WL, levels = c("WW", 660, 450)),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
         Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4"))) |>
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL))) +
  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
   geom_text(aes(x = 500000, y = 0.75, label = paste(ModelType), show.legend = FALSE)
  ) +
     scale_colour_manual(values = MCMIXColours) +
   scale_shape_manual(values = PhotoperiodShapes)  +
  facet_grid(rows = vars(O2_uM), cols = vars(Strain)) +
    labs(title = "New single fit for each [O2]- photoperiods that were significantly different were removed from single fit") +
  theme_bw()

StrainO2filteredPhotoperiod_PlattLmModel |>
  unnest(Predict, data) |>

  mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
   geom_text(aes(x = 500000, y = 0.75, label = paste(ModelType), show.legend = FALSE)
  ) +
     scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
    labs(title = "Photoperiods included in the single fit for each [O2]") +
  theme_bw()

# ANOVA on new model with significantly different fits removed from the single fit.
```{r compare 1 fit of all photoperiod to each photoperiods using platt or lm}

# make wider to join with DF that contains the 1 fit through all photoperiods
Wider_Photoperiods <- StrainO2Photoperiod_PlattLmModel %>% 
  select(Strain, Photoperiod, O2_uM, Model, Predict) %>% 
  pivot_wider(names_from = Photoperiod, values_from = c(Model, Predict))

# this contains 1 fit through all photoperiods, the photoperiods with no growth were filtered out.
AllPhotoperiods <- StrainO2filteredPhotoperiod_PlattLmModel %>% 
  select(Strain, O2_uM, Model, Predict) %>% 
 rename(All = 'Model',
        Predict_all = 'Predict')

AllFitsCombined_filtered <- left_join(Wider_Photoperiods, AllPhotoperiods)

ANOVA_AllPhotoperiods <- AllFitsCombined_filtered %>% 
  mutate(twelve = `12`,
         four = `4`,
         eight = `8`,
         sixteen = `16`) %>%
  mutate(fourvsAll = map(map2(four, All, possibly(anova, otherwise = NULL)), tidy),
         eightvsAll = map(map2(eight, All, possibly(anova, otherwise = NULL)), tidy),
         twelvevsAll = map(map2(twelve, All, possibly(anova, otherwise = NULL)), tidy),
         sixteenvsAll = map(map2(sixteen, All, possibly(anova, otherwise = NULL)), tidy)) %>% 
  select(Strain, O2_uM, fourvsAll, eightvsAll, twelvevsAll, sixteenvsAll) %>% 
  pivot_longer(cols = c(fourvsAll, eightvsAll, twelvevsAll, sixteenvsAll)) %>% 
  unnest(value, keep_empty = TRUE) %>% 
  filter(is.na(term) & is.na(p.value) |
           !is.na(term) & !is.na(p.value)) %>%
  select(Strain, O2_uM, name, p.value) %>% 
  separate(name, into = c("Photoperiod1", "AllPhotoperiod"), sep = "vs")

ANOVA_AllPhotoperiods %>% 
  mutate(Photoperiod1 = as.numeric(case_when(Photoperiod1 == 'four' ~ 4,
                                  Photoperiod1 == 'eight' ~ 8,
                                  Photoperiod1 == 'twelve' ~ 12,
                                  Photoperiod1 == 'sixteen' ~ 16)),
         O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313"))) %>%
    # mutate(Photoperiod1 = factor(Photoperiod1, levels = c('four','eight', 'twelve', 'sixteen'))) %>% 
  ggplot() +
  geom_point(aes(x = Photoperiod1, y = AllPhotoperiod), data = . %>% filter(`p.value` < 0.05)) +
  geom_text(aes(x = Photoperiod1, y = AllPhotoperiod), data = . %>% filter(`p.value` > 0.05), label = "ns") +
  geom_text(aes(x = Photoperiod1, y = AllPhotoperiod), data = . %>% filter(is.na(`p.value`)), label = "NA") +
  facet_grid(rows = vars(O2_uM), cols = vars(Strain)) +
  labs(title = "ANOVA compare all models",
       caption = "NA = atleast one model did not fit due to lack of data points; 
       ns = not significantly different from all photoperiod model (same); 
       dot = significantly different from all photoperiod model")

@@

@@

@@

  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
    geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 1, alpha = 0.8) +

@@

PURPARStrainO2PhotoNestModels |>
  filter(!map_lgl(GRCplatt_Model, is.null)) |>
  unnest(GRCplatt_Predict, data) |>
   filter(Strain == "SS120") %>%
  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
         OxygenLabel = "Oxygen Concentration (µM)",
         Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4" ))) %>%
  ggplot() +

>>>>

# model with dummy dark, 0 PAR,  growth rates. Also removed data if no growth occurred for an O2 and photoperiod combination so that the model including all photoperiods would not be skewed towards zero. As per Amanda and Doug's advice, filtered out PUR d-1 above 2.0e+06 because only photoperiods greater than 4 hrs have PUR d-1 above.
PURPARStrainO2NestModels <- PURPARFits_dummy |>
  mutate(remove = case_when(Strain == "MED4" & Photoperiod == 4 ~ 1,
                            Strain == "MED4" & O2_uM == 25 & Photoperiod == 8 & WL == "WW" ~ 1,
                            Strain == "MIT9313" & O2_uM == 2.5 & Photoperiod == 16 ~ 1,
                            Strain == "MIT9313" & O2_uM == 2.5 & Photoperiod == 12 & WL == "WW" ~ 1,
                            Strain == "SS120"  & O2_uM == 2.5 & Photoperiod %in% c(16,8,4) ~ 1,
                            Strain == "SS120"  & O2_uM == 25 & Photoperiod %in% c(16) & WL == 450 ~ 1,
                            Strain == "SS120"  & O2_uM == 250 & Photoperiod %in% c(4) & WL == 450 ~ 1,
                            TRUE ~ 0)) |>
   filter(remove == 0) |>
          # PURPhotonDose_day <= 2.0e+06) |>
  nest(data = -c("Strain","O2_uM")) |>
  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
                              data = .x,
                              start = list(a = 1e-7, b = 1e-8, Pmax = 1), 
                              lower = c(0, 0, 0),
                              upper = c(1,1,100),
                              control = list(maxiter = 500)
                         ), NULL)
                         )
         ) |>
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         ) |>
  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
                              data = .x,
                              start = LinEqnStart
                         ), NULL)
                         )
         ) |>
  mutate(GRClm_Param = map(GRClm_Model, tidy),
         GRClm_Predict = map(GRClm_Model, possibly(augment)),
         GRClm_Glance = map(GRClm_Model, possibly(glance))
         )

# Nest all data before photoperiods with no growths were filtered out
NoFilter <- PURPARFits_dummy |>
   # filter(PURPhotonDose_day <= 2.0e+06) |>
  mutate(Photoperiod_all = Photoperiod) %>% 
  nest(Data_all = -c("Strain","O2_uM"))

 # Join nested df with all data to df containing filtered data 
  PURPARStrainO2NestModels <- full_join(PURPARStrainO2NestModels, NoFilter) %>% 
    rename(Data_filtered = 'data')

remove(NoFilter)

@@

PURPARStrainO2PhotoNestModels <- PURPARFits_dummy |>
   # filter(PURPhotonDose_day <= 2.0e+06) |>
 nest(data = -c("Strain","O2_uM", "Photoperiod")) |>
  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
                              data = .x,
                              start = list(a = 1e-8, b = 1e-9, Pmax = 1),
                              lower = c(-0, 0, 0),
                              upper = c(1,1,100),
                              control = list(maxiter = 500)
                         ), NULL)
                         )
         ) |>
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         ) |>
  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
                              data = .x,
                              start = LinEqnStart
                         ), NULL)
                         )
         ) |>
  mutate(GRClm_Param = map(GRClm_Model, tidy),
         GRClm_Predict = map(GRClm_Model, possibly(augment)),
         GRClm_Glance = map(GRClm_Model, possibly(glance))
         )

@@

@@

PURPARStrainO2NestModels|>
  filter(!map_lgl(GRCplatt_Model, is.null)) |>
  unnest(GRCplatt_Predict, Data_filtered) |>
   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
  facet_grid(rows = vars(O2_uM), cols = vars(Strain)) + 
  labs(title = "PURPARStrainO2NestModels Platt") +
  theme_bw()

@@

# O2 nested data frame containing the single fit of pooled photoperiods 
 #filter to keep platt models
KeepPlattModel <- PURPARStrainO2NestModels|>
  select(-c(GRClm_Glance, GRClm_Model, GRClm_Param, GRClm_Predict)) |>
   filter(!map_lgl(GRCplatt_Model, is.null))

#filter to keep only the models that failed to fit a platt model, fits by lm remains. 
KeepLmModel <- PURPARStrainO2NestModels|>
  filter(map_lgl(GRCplatt_Model, is.null)) |>
 select(-c(GRCplatt_Glance, GRCplatt_Model, GRCplatt_Param, GRCplatt_Predict))

@@

 remove(KeepPlattModel)
 remove(KeepLmModel)
  remove(StrainO2Photoperiod_AllModels)
  remove(StrainO2_AllModels)

@@

# Unnest predict df for each photoperiod and join with pooled fit in order to plot fitted 
```{r}

Unnest_16 <- AllFitsCombined %>% 
  select(c(Strain, O2_uM, Predict_16)) %>%  
  unnest(Predict_16, keep_empty = TRUE) %>% 
  mutate(FitCategory = "sixteen",
         Photoperiod = 16)

Unnest_12 <- AllFitsCombined %>% 
  select(c(Strain, O2_uM, Predict_12)) %>%  
  unnest(Predict_12, keep_empty = TRUE) %>% 
  mutate(FitCategory = "twelve",
         Photoperiod = 12)

Unnest_8 <- AllFitsCombined %>% 
  select(c(Strain, O2_uM, Predict_8)) %>%  
  unnest(Predict_8, keep_empty = TRUE) %>% 
  mutate(FitCategory = "eight",
         Photoperiod = 8)

Unnest_4 <- AllFitsCombined %>% 
  select(c(Strain, O2_uM, Predict_4)) %>%  
  unnest(Predict_4, keep_empty = TRUE) %>% 
  mutate(FitCategory = "four",
         Photoperiod = 4)

Unnest_pooled <- AllFitsCombined %>% 
  select(c(Strain, O2_uM, Predict_all, Data_all)) %>% 
  # unnest(Data_all, keep_empty = TRUE) %>% 
  unnest(Predict_all, keep_empty = TRUE) %>% 
  mutate(FitCategory = "Pooled")

ForFitPlots <- bind_rows(Unnest_pooled, Unnest_16, Unnest_12, Unnest_8, Unnest_4)

remove(Unnest_16, Unnest_12, Unnest_8, Unnest_4, Unnest_pooled)

ForFitPlots <- left_join(ForFitPlots, ANOVA_AllPhotoperiods %>% select(Strain, O2_uM, Photoperiod1, pvalue), by = c("Strain", "O2_uM", "FitCategory" = "Photoperiod1"))

@@

  geom_line(aes(x = PURPhotonDose_day, y = .fitted), data = . %>% filter(FitCategory == "Pooled"), size = 2, color = "Blue") + 
  geom_line(aes(x = PURPhotonDose_day, y = .fitted, linetype = "twodash"), data = . %>% filter(FitCategory == "sixteen" & O2_uM == 25), size = 0.5) +
  geom_line(aes(x = PURPhotonDose_day, y = .fitted, linetype = "dotdash"), data = . %>% filter(FitCategory == "eight"), size = 0.5) +
  geom_line(aes(x = PURPhotonDose_day, y = .fitted,  linetype = "aa"), data = . %>% filter(FitCategory == "four"), size = 0.5) +
  # geom_line(aes(x = PURPhotonDose_day, y = .fitted, shape = as.factor(Photoperiod), linetype = as.factor(Photoperiod)), data = . %>% filter(FitCategory == "four"), size = 0.5) +
 # labs(title = "MED4", y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +

@@

   scale_linetype_manual(values = c("twodash", "dotdash", "aa"),labels = c("16 hr", "8 hr", "4 hr")) +

@@

@@

# TESTing additions to GGplot objects

@@

TestAddition <- StrainO2filtered_PlattLmModel |>
  unnest(Predict, Data_filtered) |>
         Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4" )),
  geom_point(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
    geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.8) +
  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`, linetype = "solid"), size = 2, color ="blue") + 

TestAddition

AddPhotoperiod <- TestAddition %>%

@@

  geom_point(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
    geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.8) +

@@

  ggplot()+
  geom_point(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
    geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.8) +
